---
title: "Check order effects Rscript"
output: html_document
---

```{r packages}
library(tidyverse)     # create plots with ggplot, manipulate data, etc.
library(broom.mixed)   # convert regression models into nice tables
library(modelsummary)  # combine multiple regression models into a single table
library(lme4)          # model specification / estimation 
library(lmerTest)      # provides p-values in the output
library(ggpubr)        # stile feature of ggplot
```

## Data Cleaning

Import data.
```{r import}
d <- read_csv("./data/order.csv")
head(d)

# delete first two rows
d <- d[3:208,]
```
Exclude participants that failed the attention check. 
```{r attention}
# attention check
# to see different answers given (i.e.levels), transform into factor
d$attention <- as.factor(d$attention)
# check levels to see different answer types
levels(d$attention) 
```
All levels are some variation of "I pay attention", so we do not exclude any participants. 

For now, the data is in a wide format where each combination of stimulus item and dependent variable has its own column. We need to "tidy" the data. 
```{r}
d <- d %>% 
  # build an easy-to-read ID variable for subjects
  mutate(ID = as.factor(1:nrow(.))) %>% 
  # order data by subjects
  arrange(ID) %>% 
  # from wide to long format
  gather(item, score, conv_large_guess_a_4:noconv_small_comp_b...91,
               factor_key=TRUE) %>% 
  # seperate variables 
  separate(item, into = c("convergence", "number", "dependent_variable",
                          "variant"), convert = T, sep = "\\_")  %>% 
  # remove NA's
  filter(!is.na(score)) %>% 
  # make sure data is still ordered by participants
  arrange(ID) %>% 
  # The variable "variant" that distinguishes between the two items of the same
  # condition did not come as intended. Without changing it, we won't be able
  # to "spread" our dependent variables (DV)
  mutate(variant = rep(c("a", "b"), each = 3, length.out = nrow(.))) %>% 
  # now for each subject, each condition and each variant the three DVs
  # can be assigned
  pivot_wider(names_from = dependent_variable, values_from = score) %>% 
  # so far, all variables are coded characters (see e.g. str(d))
  # we want our dependent variables to be numeric
  mutate(competence = as.numeric(comp),
         guess = as.numeric(guess), 
         confidence = as.numeric(conf))
```

In the qualtrics output, the the order of each condition-stimulus pair is coded as a separate variable (i.e. column). The names of these variables are given by qualtrics internally. We need to manually check in the qualtrics flow diagram (by activating to see the flow names, top right corner), which condition-stimulus pair corresponds to which flow name (i.e. the variable/column name that appears in our data set). Once we have done this, we bring our data frame in the long format just like above. We then only select those values of the order variable that correspond to our stimuli (we build an identifier variable for stimulus beforehand and check row by row whether this identifier corresponds to the order variable). 
```{r}
d <- d %>% 
  rename(sample1 = FL_5_DO_FL_13,
         sample2 = FL_5_DO_FL_14,
         sample3 = FL_5_DO_FL_37) %>% 
  gather(sample, indicator, sample1:sample3,
               factor_key=TRUE) %>% 
  # remove NA's
  filter(!is.na(indicator)) %>% 
  # build an identifier variable to later check against
  mutate(stimulus = paste(convergence, number, variant, sample, sep = "_")) %>%
  # rename flow names to later check against identifier variable
  rename(conv_large_a_sample1_order = FL_24_DO_FL_41,
         conv_large_b_sample1_order = FL_24_DO_FL_44,
         conv_small_a_sample1_order = FL_24_DO_FL_46,
         conv_small_b_sample1_order = FL_24_DO_FL_49,
         noconv_large_a_sample1_order = FL_24_DO_FL_52,
         noconv_large_b_sample1_order = FL_24_DO_FL_55,
         noconv_small_a_sample1_order = FL_24_DO_FL_58,
         noconv_small_b_sample1_order = FL_24_DO_FL_61,
         conv_large_a_sample2_order = FL_15_DO_FL_64,
         conv_large_b_sample2_order = FL_15_DO_FL_67,
         conv_small_a_sample2_order = FL_15_DO_FL_70,
         conv_small_b_sample2_order = FL_15_DO_FL_72,
         noconv_large_a_sample2_order = FL_15_DO_FL_74,
         noconv_large_b_sample2_order = FL_15_DO_FL_76,
         noconv_small_a_sample2_order = FL_15_DO_FL_78,
         noconv_small_b_sample2_order = FL_15_DO_FL_81,
         conv_large_a_sample3_order = FL_38_DO_FL_83,
         conv_large_b_sample3_order = FL_38_DO_FL_86,
         conv_small_a_sample3_order = FL_38_DO_FL_88,
         conv_small_b_sample3_order = FL_38_DO_FL_90,
         noconv_large_a_sample3_order = FL_38_DO_FL_92,
         noconv_large_b_sample3_order = FL_38_DO_FL_94,
         noconv_small_a_sample3_order = FL_38_DO_FL_96,
         noconv_small_b_sample3_order = FL_38_DO_FL_98,
         ) %>% 
  # frow wide to long
  gather(stimulus_order, order_indicator, 
         conv_large_a_sample1_order:noconv_small_b_sample3_order,
               factor_key=TRUE) %>% 
  # remove NA's
  filter(!is.na(order_indicator)) %>% 
  # order data by participants
  arrange(ID) %>% 
  mutate(stimulus_order = as.character(stimulus_order),
         order_indicator = as.numeric(order_indicator),
         # compare stimulus identifier column with order identifier column
         # only keep the order values where they match
         order = ifelse(paste0(stimulus, "_order") == 
                          stimulus_order, order_indicator, NA)) %>% 
  # remove NA's
  filter(!is.na(order)) %>% 
  # get rid of building variables 
  select(-c("indicator", "stimulus", "stimulus_order", "order_indicator"))

```

To see if there are any weird values, we inspect the distributions of the dependent variables.
```{r}
# competence
ggplot(d, aes(x = competence)) +
  geom_histogram()# seems like 7s have been coded as 8s

# confidence
ggplot(d, aes(x = confidence)) +
  geom_histogram()# same, 7s have been coded as 8s

# guess
ggplot(d, aes(x = guess)) +
  geom_histogram() # all guesses are coded withing range, looks good
```
For the two Likert scale measures (`confidence` and `competence`) The maximum of the scale has been coded as `8` instead of `7`. 

```{r}
d <- d %>% 
  mutate(competence = ifelse(competence == 8, 7, competence), 
         confidence = ifelse(confidence ==8, 7, confidence))

# check again
ggplot(d, aes(x = competence)) +
  geom_histogram()# looks good

ggplot(d, aes(x = confidence)) +
  geom_histogram()# looks good
```
## Check order effects

Here are the means for the convergence conditions conditional on whether they were first or last in order.
```{r}
d %>% 
  filter(convergence == "conv", order == 1 ) %>% 
  summarise(mean_confidence_convergence_first_element = mean(confidence), 
            mean_competence_convergence_first_element = mean(competence))

d %>% 
  filter(convergence == "conv", order == 8 ) %>% 
  summarise(mean_confidence_convergence_last_element = mean(confidence), 
            mean_competence_convergence_last_element = mean(competence))

d %>% 
  filter(convergence == "noconv", order == 1 ) %>% 
  summarise(mean_confidence_noconvergence_first_element = mean(confidence), 
            mean_competence_noconvergence_first_element = mean(competence))

d %>% 
  filter(convergence == "noconv", order == 8 ) %>% 
  summarise(mean_confidence_noconvergence_last_element = mean(confidence), 
            mean_competence_noconvergence_last_element = mean(competence))
```

Here is a t-test for competence between convergent and non-convergent based on stimuli ratings that came _first_ in order.

```{r}
d_first_order <- d %>% 
  filter(order == 1)

first_order_model <- lm(competence ~ convergence, data = d_first_order)
summary(first_order_model)

d_last_order <- d %>% 
  filter(order == 8)

last_order_model <- lm(competence ~ convergence, data = d_last_order)
summary(last_order_model)
```









