# Experiment 2 {#exp2}

\FloatBarrier

```{r exp2-conditions}
# We manipulated informational dependency. According to the condition, players read a different introduction before seeing a set of estimates (see Table \@ref(tab:exp2-conditions)).

# The different introductions that participants read before seeing the sets of estimates, according to the conditions 
# data.frame(
#   Condition = c("Independence", "Discussion"),
#   Description = c(
#     "Players are asked to make completely independent decisions – they cannot see each other’s estimates, or talk with each other before giving their estimates.",
#     "Players are asked to talk with each other about the game at length before giving their estimates."
#   )
# ) %>% 
#   apa_table(align = c("m{3cm}", "m{10cm}")) 
```

## Attention check

Imagine you are playing video games with a friend and at some point your friend says: “I don’t want to play this game anymore! To make sure that you read the instructions, please write the three following words "I pay attention" in the box below. I really dislike this game, it's the most overrated game ever.”

Do you agree with your friend? (Yes/No)

## Results

Figure \@ref(fig:exp2-plot) visualizes the results and table \@ref(tab:exp2-table) contains descriptive results.

```{r exp2-table}
exp2 %>% 
  group_by(independence) %>% 
  summarise(across(c(competence, confidence), list(mean = mean, sd = sd))) %>% 
  rounded_numbers() %>% 
  mutate(Accuracy = paste0(confidence_mean, " (sd = ", confidence_sd, ")"),
         Competence = paste0(competence_mean, " (sd = ", competence_sd, ")")
         ) %>% 
  rename(Independence = independence) %>% 
  select(Independence, Accuracy, Competence) %>% 
  apa_table()
```

(ref:exp2-plot) Distributions of accuracy and competence by level of informational dependency.

```{r exp2-plot, fig.cap="(ref:exp2-plot)"}
# make mean data for plot
x_nudge <- 0.8

means <- exp2 %>%
  group_by(independence) %>%
  summarize(confidence = mean(confidence), 
            competence = mean(competence)) %>% 
  pivot_longer(c(confidence, competence), 
               names_to = "outcome", 
               values_to = "value") %>% 
  mutate(x_position = ifelse(independence == "dependent", value + x_nudge, 
                                value - x_nudge)) 

confidence_plot <- ggplot(data=exp2, aes(x=confidence, fill=independence)) +
  # density plot
  geom_density(adjust=3, alpha=.6) +
 # mean lines
  geom_vline(data=means %>% 
               filter(outcome == "confidence"), 
             aes(xintercept = value, 
                 color = independence),
             show.legend = FALSE,
             linetype="dashed") +
  geom_label(data = means %>% 
               filter(outcome == "confidence"), 
             aes(x = x_position, y = 0.3, 
                 label =  paste("mean", round(value, digits = 2),
                                sep = " = ")), 
             alpha = 0.6, show.legend = FALSE, size = 3
            ) +
  # scales
  scale_x_continuous(name = "Accuracy (confidence) ratings", breaks = seq(1, 7), 
                     limits=c(1, 7)) +
  scale_y_continuous(name = "Density", limits=c(0, 0.4)) +
  scale_fill_brewer(palette = "Accent",
                    direction = 1) +
  scale_color_brewer(palette = "Accent",
                    direction = 1) +
  guides(fill = guide_legend(title = NULL)) +
  plot_theme 

competence_plot <- ggplot(data=exp2, aes(x=competence, fill=independence)) +
  # density plot
  geom_density(adjust=3, alpha=.6) +
 # mean lines
  geom_vline(data=means %>% 
               filter(outcome == "competence"), 
             aes(xintercept = value, 
                 color = independence),
             show.legend = FALSE,
             linetype="dashed") +
  geom_label(data = means %>% 
               filter(outcome == "competence"), 
             aes(x = x_position, y = 0.3, 
                 label =  paste("mean", round(value, digits = 2),
                                sep = " = ")), 
             alpha = 0.6, show.legend = FALSE, size = 3
            ) +
  # scales
  scale_x_continuous(name = "Competence ratings", breaks = seq(1, 7), 
                     limits=c(1, 7)) +
  scale_y_continuous(name = "Density", limits=c(0, 0.4)) +
  scale_fill_brewer(palette = "Accent",
                    direction = 1) +
  scale_color_brewer(palette = "Accent",
                    direction = 1) +
  guides(fill = guide_legend(title = NULL)) +
  plot_theme 

figure <- ggarrange(confidence_plot, 
                    competence_plot + 
                      theme(axis.text.y = element_blank(),
                            axis.ticks.y = element_blank(),
                            axis.title.y = element_blank()), 
                    common.legend = T) +
  theme(legend.position="top") 
figure
```


