---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.retina = 3
)

yaml_metadata <- rmarkdown::yaml_front_matter(here::here("paper.Rmd"))
title <- yaml_metadata$title
abstract <- yaml_metadata$abstract
```

# `r title`

---

## Abstract

`r abstract`

---

## How to download and replicate

To reproduce the findings and re-run the analysis, do the following:

1. Download and install this repository. You can use GitHub to clone or fork the repository (see the green "Clone or download" button at the top of the GitHub page).
2. Open `consensus_trust.Rproj` to open an [RStudio Project](https://r4ds.had.co.nz/workflow-projects.html).
3. Within the RStudio Project, open the `paper.Rmd` file and run it. 

Please find the [session info below](#session-info).

*Estimated installation time* : If you have R and Rstudio installed, then adding additional packages required in our R scripts is quick (a couple of minutes)

*Estimated run time*: Rendering the `anonymized.Rmd` document takes about 2mins on our machine (see [session info](#session-info))


## Files glossary {#glossary}

- `appendix*` files contain the appendices that are automatically added `paper.Rmd` when rendering the file.
- `Cogsci*` files are documents used to generate a shorter version of our paper submitted for the CogSci 2024 conference. 
- `Experiment*` folders contain all files related to the respective experiment. The `/data` folders contain the raw data (`qualtrics.csv`) and cleaned data (`cleaned.csv`). The cleaning can be reproduced by running the `cleaning.Rmd`. `Experiment_1` and `Experiment_4` also contain the code for the simulations (`model.Rmd`) and several data files with simulated data. 
- `functions/` folder contains functions that we rely upon in our analysis scripts. To keep the `paper.Rmd` document neat and readable, we wrote all lengthy code bits as external functions.
- figures includes images used in the `paper.Rmd` file
- `howwise_0131.pdf` is the final submission to the CogSci 2024 conference, based on the raw files but edited in [overleaf](https://www.overleaf.com/). 
- `output` folder lists all figures generated by the `paper.Rmd` file as `.png` and `.pdf` files.
- `paper.pdf` is the rendered version of `paper.Rmd`
- `references.bib` contains the references
- `stimuli` folder contains all stimuli

## Session info {#session-info}

```{r, echo=FALSE}
sessionInfo()
```

## Licenses

**Text and figures:** All prose and images are licensed under Creative Commons ([CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)).

**Code:** All code is licensed under the [MIT License](LICENSE.md).
