---
title: "Data cleaning experiment 2"
author: "Jan Pfänder, Hugo Mercier"
date: "2023-03-09"
output: 
  html_document: 
    keep_md: yes
---

```{r packages, message=FALSE}
library(tidyverse)     # create plots with ggplot, manipulate data, etc.
library(broom.mixed)   # convert regression models into nice tables
library(modelsummary)  # combine multiple regression models into a single table
library(lme4)          # model specification / estimation 
library(lmerTest)      # provides p-values in the output
library(ggpubr)        # stile feature of ggplot
library(gghalves)      # do special plots in ggplot
library(kableExtra)    # for tables
```

## Import data

```{r import}
d <- read_csv("./data/qualtrics.csv")
head(d)

# delete first two rows
d <- d[3:202,]
```


## Attention checks

```{r attention}
# attention check
# to see different answers given (i.e.levels), transform into factor
d$attention <- as.factor(d$attention)
# check levels to see different answer types
levels(d$attention) 
```
All levels are some variation of "I pay attention", so we do not exclude any participants. 

## Variable name correction

There was a coding problem in the data - a variable that start with "dep_conf_b_III" appears twice. Looking at the qualtrics, one of them should in fact identify "dep_guess_b_III", i.e. the numeric guess instead of a confidence rating. We identify this column looking at the values. Large values in the thousands indicate it's a guess and not a confidence rating. 

```{r}
d %>% 
  select(starts_with("dep_conf_b_III"))
```

The output indicates that "dep_conf_b_III_4" captures the guess and should be named "dep_guess_b_III". 

```{r}
d <- d %>% 
  rename(dep_guess_b_III = dep_conf_b_III_4)
```

## Re-shaping data

For now, the data is in a wide format where each combination of stimulus item and dependent variable has its own column. We need to "tidy" the data. 

```{r}
d <- d %>% 
  # build an easy-to-read ID variable for subjects
  mutate(ID = as.factor(1:nrow(.))) %>% 
  # order data by subjects
  arrange(ID) %>% 
  # from wide to long format
  gather(item, score, dep_guess_b_I_4:dep_comp_a_III,
               factor_key=TRUE) %>% 
  # seperate variables 
  separate(item, into = c("independence", "dependent_variable", 
                          "stimulus_variant", "sample"), 
           convert = T, sep = "\\_")  %>% 
  # remove NA's
  filter(!is.na(score)) %>% 
  # make sure data is still ordered by participants
  arrange(ID) %>%
  # now for each subject, each condition and each variant the three DVs
  # can be assigned
  pivot_wider(names_from = dependent_variable, values_from = score) %>% 
  # so far, all variables are coded characters (see e.g. str(d))
  # we want our dependent variables to be numeric
  mutate(competence = as.numeric(comp),
         guess = as.numeric(guess), 
         confidence = as.numeric(conf))
```

## Recoding some values

To see if there are any weird values, we inspect the distributions of the dependent variables.
```{r}
# competence
ggplot(d, aes(x = competence)) +
  geom_histogram()# seems like 7s have been coded as 8s

# confidence
ggplot(d, aes(x = confidence)) +
  geom_histogram()# same, 7s have been coded as 8s

# guess
ggplot(d, aes(x = guess)) +
  geom_histogram() # all guesses are coded withing range, looks good
```

For the two Likert scale measures (`confidence` and `competence`) the maximum of the scale has been coded as `8` instead of `7`. 

```{r}
d <- d %>% 
  mutate(competence = ifelse(competence == 8, 7, competence), 
         confidence = ifelse(confidence ==8, 7, confidence))

# check again
ggplot(d, aes(x = competence)) +
  geom_histogram()# looks good

ggplot(d, aes(x = confidence)) +
  geom_histogram()# looks good
```

## Recoding factors

Lastly, we recode the `independence` variable. 

```{r}
# recode independence
d <- d %>%
  mutate(
    independence = ifelse(independence == "indep", "independent", "dependent"),
    independence = as.factor(independence),
    independence = fct_relevel(independence, "dependent", "independent")
    )
```

## Rename demographics

```{r}
d <- d %>% 
  rename(education = Q5, 
         age = Q4,
         gender = Q3) %>% 
  mutate(gender = case_when(gender == 1 ~ "male", 
                            gender == 2 ~  "female", 
                            .default = NA)
         )
```

## Export data

```{r}
write_csv(d, "data/cleaned.csv")
```





