---
title: 
- "Analysis Experiment 6: Is convergence less trustworthy when informants are biased?"
author: 
- "Hugo Mercier, Jan Pfänder" 
date: "2023-02-02"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, error = TRUE) 
```

```{r, message=FALSE}
library(tidyverse) # for everything
library(tidyr) # some additional, neat tidy reshaping functions
library(lme4) # for linear mixed models
library(lmerTest) # p-values for mixed models
library(broom) # for tidy outputs of regressions
library(broom.mixed) # for tidy outputs of linear mixed models
library(ggridges) # for plots
library(gghalves) # for plots
library(ggbeeswarm) # Special distribution-shaped point jittering
library(scales)  # for nice axis labels
library(modelsummary) # regression tables
library(patchwork) # combine plots
library(ggrepel) # fit labels in plots 
```

### Some themes and functions

```{r, echo=FALSE}
# round numbers from models
rounded_numbers <- function(x) mutate_if(x, is.numeric, round, 3)

#set general theme for plots
plot_theme <- theme_minimal(base_size = 12) +
  theme(# Bold, bigger title
        plot.title = element_text(face = "bold", size = rel(1.7)),
        # Plain, slightly bigger subtitle that is grey
        plot.subtitle = element_text(face = "plain", size = rel(1.3), color = "grey70"),
        # Bold legend titles
        legend.title = element_text(face = "bold"),
        # Bold axis titles
        axis.title = element_text(face = "bold"))
```

### Read data
```{r, message=FALSE}
# read data
d <- read_csv("./data/cleaned.csv")
```

### H1a: Participants perceive an estimate of an independent informant as more accurate the more it converges with the estimates of other informants.

To test this hypothesis, we only consider participants assigned to the `independent` condition.

We use a linear mixed effect model with random intercept and random slope per participant.

In all our models we treat `convergence` as a continuous variable. We will, however, include robustness checks where we treat convergence as a categorical variable. 

```{r, warning=FALSE, message=FALSE}
# models for accuracy

# random intercept and slope by participants
model_accuracy_independent <- lmer(accuracy ~ convergence + (1 + convergence | id), 
                       data = d %>% filter(independence == "independent"))
```


### H1b: Participants perceive an independent informant as more competent the more their estimate converges with the estimates of other informants.

We will proceed in the same way for `competence` as we did for `accuracy` above.

```{r, warning=FALSE, message=FALSE}
# models for competence

# random intercept and slope by participants
model_competence_independent <- lmer(competence ~ convergence + 
                           (1 + convergence | id), 
                         data = d %>% filter(independence == "independent"))
```

### H2a: The effect of convergence on accuracy (H1a) is more positive in a context where informants are independent compared to when they are biased (i.e. share a conflict of interest to pick a given answer). 

To test this hypothesis, we only consider the full data.

The resulting estimate of the interaction term will provide the test for our hypothesis. 

```{r, warning=FALSE, message=FALSE}
# models for accuracy

# random intercept and slope by participants
model_accuracy <- lmer(accuracy ~ convergence + independence + 
                            independence*convergence + (1 + convergence | id), 
                       data = d)
```


### H2b: The effect of convergence on competence (H1b) is more positive in a context where informants are independent compared to when they are biased (i.e. share a conflict of interest to pick a given answer).

To test this hypothesis, we only consider the full data.

The resulting estimate of the interaction term will provide the test for our hypothesis. 

```{r}
# models for competence

# random intercept and slope by participants
model_competence <- lmer(competence ~ convergence + independence + 
                            independence*convergence + (1 + convergence | id), 
                       data = d)

```

Show all results
```{r, echo=FALSE}
models <- list("Accuracy (independent only)" = model_accuracy_independent, 
               "Competence (independent only)" = model_competence_independent, 
               "Accuracy" = model_accuracy, 
               "Competence" = model_competence)
modelsummary::modelsummary(models, stars = TRUE)
```


# Robustness checks

In the models above, we treated convergence as a continuous variable. Based on the different levels, we will build a categorical variable, `convergence_categorical`. 

```{r, echo=FALSE}
# make a categorical variable from `convergence`
d <- d %>% 
  mutate(convergence_categorical = recode_factor(convergence, 
                                                 `0` = "opposing majority", 
                                                 `1` = "divergence", 
                                                 `2` = "majority", 
                                                 `3` = "consensus",
                                                 .default = NA_character_)
         )

levels(d$convergence_categorical)
  
```


We run the same models outlined in the hypotheses section, but replacing `convergence` with `convergence_categorical`. This also allows us to inspect heterogeniety in differences between levels (with respect to the baseline, i.e. "opposing majority"). 


### Plots

#### Independence Condition only

```{r, echo=FALSE}
# plot for accuracy
plot_accuracy <- ggplot(d %>% filter(independence == "independent"),
       aes(x = convergence_categorical, y = accuracy, fill = convergence_categorical)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .8,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  labs(x = "Convergence", y = "Accuracy") +
  scale_fill_viridis_d(option = "plasma", begin = 0.1) +
  guides(fill = FALSE) +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

```{r, echo=FALSE}
# plot for competence
plot_competence <- ggplot(d %>% filter(independence == "independent"),
       aes(x = convergence_categorical, y = competence, fill = convergence_categorical)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .8,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 1, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  labs(x = "Convergence", y = "Competence") +
  scale_fill_viridis_d(option = "plasma") +
  guides(fill = FALSE) +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

```{r, echo=FALSE}
plot_accuracy + plot_competence
```

#### Interaction

```{r, echo=FALSE}
# plot for accuracy
plot_accuracy <- ggplot(d,
       aes(x = convergence_categorical, y = accuracy, fill = independence)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .4,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 2, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  labs(x = "Convergence", y = "Accuracy", fill = NULL) +
  scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

```{r, echo=FALSE}
# plot for competence
plot_competence <- ggplot(d,
       aes(x = convergence_categorical, y = competence, fill = independence)) +
  geom_half_violin(position = position_nudge(x = -.2),
                   adjust=2, alpha = .4,
                   side = "l") +
  stat_summary(fun = "mean", geom = "point", size = 2, shape = 21) +
  stat_summary(fun = "mean", geom = "line", size = 1, linetype = "dashed") +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .2) +
  # Add nice labels
  labs(x = "Convergence", y = "Competence", fill = NULL) +
  scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
  plot_theme + 
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

```{r main-plot, echo=FALSE}
ggpubr::ggarrange(plot_accuracy, plot_competence, common.legend = TRUE)
```
